CVS Installation und Konfiguration

### 2013-10-10 CM-Scripts/studentuserlist.tex
allowed file size temporarily increased

\rowcolor{yellow}\cellcolor{green}diplomand1 &alber  &Thomas Alber    &th.alber@loop.de      &Javagui/viewer/queryconstruction2 &17.06.13     &\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand2 &keberl &Katharina Rieder&keberl@web.de         &Algebras/TrajetoryAnnotation      &16.04.12     &\\

@@

\cellcolor{green}          &fpanse                   &Frank Panse     &                      &Algebras/SymbolicTrajectory       &21.12.10     &05.03.12\\

@@

\cellcolor{green}          &nvoget                   &Nicolai Voget   &                      &Algebras/OrderedRelation          &             &21.12.10\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand5   &zacher &Dirk Zacher     &dirk.zacher@fernuni-hagen.de&Algebras/Tile               &18.04.13     &\cellcolor{red}Laptop\\

@@

\cellcolor{red}            &mroth                    &Matthias Roth   &Fernstudium@planet-roth.de&Algebras/MapMatching          &21.11.11     &21.12.12\\

@@

\cellcolor{green}diplomand10&willmes                 &Gero Willmes    &student@harpspieler.de&Optimizer/LargeQueries            &29.11.11     &21.12.12\\

@@

\cellcolor{green}          &herkert                  &A. Herkert      &                      &LargeQueries                      &01.03.10     &08.02.11\\

@@

\cellcolor{green}diplomand11&schrage                 &Michael Schrage &schragman@googlemail.com&JDBC                            &23.12.11     &21.12.12\\

@@

\cellcolor{green}          &danbro                   &Daniel Brockmann&                      &Algebras/UGrid                    &14.04.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand13&nidzwetzki&Jan Nidzwetzki&nidzwetzki@gmx.de    &Algebras/CostEstimation           &18.04.12     &\\

@@

\cellcolor{green}diplomand16&jmoeller                &Jasmin Moeller  &JasminMoeller@gmx.de  &Algebras/Cluster2                 &28.06.12     &21.12.12\\

>>>>

\rowcolor{yellow}\cellcolor{red}diplomand1   &alber  &Thomas Alber    &th.alber@loop.de      &Javagui/viewer/queryconstruction2 &17.06.13     &\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand2   &ahmed  &Jasmine Ahmed   &j.ahmed@gmx.de        &Javagui/viewer/update2            &19.06.13     &\\

@@

\cellcolor{red}            &keberl                   &Katharina Rieder&keberl@web.de         &Algebras/TrajetoryAnnotation      &16.04.12     &19.06.13\\

@@

\cellcolor{red}            &fpanse                   &Frank Panse     &                      &Algebras/SymbolicTrajectory       &21.12.10     &05.03.12\\
\cellcolor{red}            &nvoget                   &Nicolai Voget   &                      &Algebras/OrderedRelation          &             &21.12.10\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand5   &zacher &Dirk Zacher     &dirk.zacher@fernuni-hagen.de&Algebras/Tile \& Algebras/Raster2&18.04.13     &\cellcolor{red}Laptop\\

@@

\cellcolor{red}            &mroth                    &Matthias Roth   &fernstudium@planet-roth.de&Algebras/MapMatching          &21.11.11     &21.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand10  &dbecker&Dirk Becker     &tyr@tyrbedarf.de      &Algebras/Cluster2                 &19.06.13     &\\

@@

\cellcolor{red}            &willmes                  &Gero Willmes    &student@harpspieler.de&Optimizer/LargeQueries            &29.11.11     &21.12.12\\
\cellcolor{red}            &herkert                  &A. Herkert      &                      &LargeQueries                      &01.03.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand11  &schroeer&Susanne Schröer&susanne@team-schroeer.com&(noch keins)                   &19.08.13     &\\

@@

\cellcolor{red}            &schrage                  &Michael Schrage &schragman@googlemail.com&JDBC                            &23.12.11     &21.12.12\\
\cellcolor{red}            &danbro                   &Daniel Brockmann&                      &Algebras/UGrid                    &14.04.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand13&nidzwetzki&Jan Nidzwetzki&knidzwetzki@gmx.de   &Algebras/CostEstimation           &18.04.12     &\\

@@

\cellcolor{green}diplomand16&jmoeller                &Jasmin Moeller  &jasminmoeller@gmx.de  &Algebras/Cluster2                 &28.06.12     &21.12.12\\
